High geomagnetic field intensity recorded by anorthosite xenoliths requires a vigorous late Mesoproterozoic geodynamo

### 2022-04-04 PNAS_manuscript/Supporting Info.tex
Updates from Overleaf

\begin{table}[]
\centering
\caption{\footnotesize{Summary paleointensity result statistics at site-level, region-level, and overall arithmetic means. The statistics names are the same as in Table \ref{tab:PINT_result}}. n represents the total number of specimen- or site- or region-level results used for calculating mean values. inc$_{tc}$ is the tilt-corrected mean inclination. Site-level means for AX6, AX8, AX10, AX11, AX12, AX13, AX16 are calculated based on specimen results. Regional means for Carlton Peak, Kennedy Creek, and Silver Bay are calculated by grouping specimen results from AX6 and AX8 and AX10, AX11 and AX13, AX12 and AX16, respectively. Overall site mean values are calculated using all site-level results in this table. Overall region-mean values are calculated using all regional mean results in this table. }
\begin{tabular}{ccccccccccc}
\hline
\multicolumn{1}{l}{}                       &               & B$_{anc}$ & n  & FRAC & GAP-MAX & MAD ($^\circ$) & DANG ($^\circ$) & inc$_{tc}$ & $\gamma$ & VDM (ZAm$^2$) \\
\hline
\multirow{7}{*}{specimen mean for sites}   & AX6           & 30.33     & 3  & 0.69 & 0.13    & 3.55           & 2.66            & 38.9       & 2.63     & 48.76         \\
                                           & AX8           & 52.4      & 3  & 0.66 & 0.17    & 4.28           & 2.15            & 40.3       & 7.3      & 83.14         \\
                                           & AX10          & 46.82     & 3  & 0.7  & 0.23    & 4.98           & 2.14            & 36.6       & 6.1      & 76.81         \\
                                           & AX12          & 38.1      & 6  & 0.75 & 0.22    & 3.26           & 2.53            & 55.2       & 5.98     & 51.31         \\
                                           & AX16          & 44.15     & 11 & 0.68 & 0.19    & 4.19           & 1.96            & 49.2       & 3.97     & 63.87         \\
                                           & AX11          & 73.34     & 7  & 0.68 & 0.19    & 3.85           & 1.82            & 35.2       & 6.63     & 121.73        \\
                                           & AX13          & 76.63     & 7  & 0.73 & 0.2     & 5.7            & 1.67            & 35.1       & 5        & 127.29        \\ 
                                           \hline
\multirow{3}{*}{specimen mean for regions} & Carlton Peak  & 43.18     & 9  & 0.68 & 0.17    & 4.27           & 2.32            & 38.6       & 5.34     & 69.57         \\
                                           & Kennedy Creek & 74.98     & 14 & 0.7  & 0.2     & 4.78           & 1.74            & 35.15      & 5.81     & 124.51        \\
                                           & Silver Bay    & 42.02     & 17 & 0.71 & 0.2     & 3.86           & 2.16            & 51.32      & 4.68     & 59.43         \\
\hline
overall site mean                          &               & 51.68     & 7  &      &         &                &                 &            &          & 81.84         \\
overall region mean                        &               & 53.39     & 3  &      &         &                &                 &            &          & 84.5         
\end{tabular}
\end{table}

>>>>

\begin{table}[]
\centering
\caption{\footnotesize{Summary paleointensity result statistics at site-level, region-level, and overall arithmetic means. The statistics names are the same as in Table \ref{tab:PINT_result}}. n represents the total number of specimen- or site- or region-level results used for calculating mean values. inc$_{tc}$ is the tilt-corrected mean inclination. Site-level means for AX6, AX8, AX10, AX11, AX12, AX13, AX16 are calculated based on specimen results. Regional means for Carlton Peak, Kennedy Creek, and Silver Bay are calculated by grouping specimen results from AX6 and AX8 and AX10, AX11 and AX13, AX12 and AX16, respectively. Overall site mean values are calculated using all site-level results in this table. Overall region-mean values are calculated using all regional mean results in this table. Independent two-sample t-test results show that site AX12 and AX16 pass the t-test at 1\% significance level; site AX11 and AX13 pass the test at 5\% significance level; region Kennedy Creek have distinguishable distributions from the other two regions; Silver Bay region and Carlton Peak region are indistinguishable at 5\% significance level.}
\begin{tabular}{ccccccccccc}
\hline
\multicolumn{1}{l}{}                       &               & B$_{anc}$ & n  & FRAC & GAP-MAX & MAD ($^\circ$) & DANG ($^\circ$) & inc$_{tc}$ & $\gamma$ & VDM (ZAm$^2$) \\
\hline
\multirow{7}{*}{specimen mean for sites}   & AX6           & 30.3     & 3  & 0.69 & 0.13    & 3.6           & 2.7            & 38.9       & 2.6     & 48.8         \\
                                           & AX8           & 52.4      & 3  & 0.66 & 0.17    & 4.3           & 2.2            & 40.3       & 7.3      & 83.1         \\
                                           & AX10          & 46.8     & 3  & 0.70  & 0.23    & 5.0           & 2.1            & 36.6       & 6.1      & 76.8         \\
                                           & AX12          & 38.1      & 6  & 0.75 & 0.22    & 3.3           & 2.5            & 55.2       & 6.0     & 51.3         \\
                                           & AX16          & 44.2     & 11 & 0.68 & 0.19    & 4.2           & 2.0            & 49.2       & 4.0     & 63.9         \\
                                           & AX11          & 73.3     & 7  & 0.68 & 0.19    & 3.9           & 1.8            & 35.2       & 6.6     & 121.7        \\
                                           & AX13          & 76.6     & 7  & 0.73 & 0.20     & 5.7            & 1.7            & 35.1       & 5        & 127.3        \\ 
                                           \hline
\multirow{3}{*}{specimen mean for regions} & Carlton Peak  & 43.2     & 9  & 0.68 & 0.17    & 4.3          & 2.3            & 38.6       & 5.3     & 69.6         \\
                                           & Kennedy Creek & 75.0     & 14 & 0.70  & 0.20     & 4.8           & 1.7            & 35.2      & 5.8     & 124.5        \\
                                           & Silver Bay    & 42.0     & 17 & 0.71 & 0.20     & 3.9           & 2.2            & 51.3      & 4.7     & 59.4         \\
\hline
overall site mean                          &               & 51.7     & 7  &      &         &                &                 &            &          & 81.8         \\
overall region mean                        &               & 53.4     & 3  &      &         &                &                 &            &          & 84.5         
\end{tabular}
\end{table}
